---
title: "Block Zero Schedule 18 January - 15th Feb 2021"
author: "Paul Matthews"
date: "08/01/2021"
output:
  html_document:
    df_print: paged
params:
  progcode: INB112
---

```{r setup, include=FALSE}
library(tidyverse)
library(vistime)
library(knitr)
library(calendar)
library(gt)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE)
blockzero <- read_csv("data/blockzero.csv")
programmes <- read_csv("data/programmes.csv")
blockzero <- blockzero[(blockzero$programme == params$progcode | blockzero$programme == 'GEN') & !is.na(blockzero$start),]
currentprog <- programmes %>% filter(code == params$progcode)
```

# `r currentprog$name`

## Block Zero Schedule : 18 January - 5th Feb 2021

*Note: Subject to Change, please check back & refresh iCal*

The online sessions will use Blackboard Collaborate. Guest access will be enabled, so you won't have to login with UWE credentials if you don't have them yet.  See [the guidance pages for support and introduction information](https://info.uwe.ac.uk/online/blackboard/students/guides/). Collaborate will work best on a PC with a Broadband connection and webcam.

*All times in GMT, UK*

```{r message=FALSE, warning=FALSE}
blockzero %>% select(start, end, content, details, link) %>% arrange(start) %>% 
  mutate(across(c(start,end), format ,"%a, %d %b %H:%M")) %>%
  mutate(link = paste0("[Join online session](", link, ")")) %>% 
  kable()
```


```{r}
blockzero %>% transmute(UID=id, DTSTART=start, DTEND=end, SUMMARY=content, DESCRIPTION = paste(details, link), DTSTAMP=format(Sys.time(), "%Y%m%dT%H%m00")) %>%
ical() %>% ic_write(file=paste0(params$progcode, "blockzero.ics"))
```

__[Get iCal](`r paste0(params$progcode, "blockzero.ics")`)__

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
blockzero %>% mutate(title=content, group=paste("Week", week(start)-2, wday(start, label=T))) %>% 
  gg_vistime(col.event="title", col.start="start", col.end="end", optimize_y = T) 
```

